The Inner Mass-Ratio Distribution of Intermediate-Mass Stars

### 2016-02-23 paper/ms.tex

TODO: Put the MCMC samples up on zenodo or something.

@@

>>>>

@@

\subsection{Supplemental Data}

In the effort of open and reproducible research, we have made several data products freely available to the community. The samples of primary and companion mass and system age are available at \url{https://zenodo.org/record/46340}. The files generated by MultiNest, which include samples from the posterior distributions described in Section \ref{sec:mrd}, are available at the same url. We additionally provide a series of python libraries and jupyter notebooks with the computer code we used for the analysis on github: \url{https://github.com/kgullikson88/BinaryInference}.
